Moral Foundations of U.S. Political News Organizations

### 2019-04-06 pilot_manuscript.Rmd
reverted some of the files that I think I screwed up

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")

>>>>

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F)
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
